Investigating Predictors for American Attitudes on Justifiability of Abortion

### 2022-06-20 Final/FinalReport.qmd
conditions code started

Conditions check

Linearity \[residual plot vs fitted values\]

Randomness

Independence \[residual plot vs id\]

>>>>

Below we will check each of the following conditions for our model:
Linearity, Constant Variance, Normality, and Independence.

```{r fit-aug}
final_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(aj ~ year + ideology + cai + godimportant +
                        respectauthority + nationalpride,
      data = abortion_data)

final_fit_aug <- augment(final_fit$fit)
```

Linearity

```{r linearity}
#| echo: false
ggplot(data = final_fit_aug, aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  labs(x = "Predicted values", y = "Residuals")
```

Constant Variance

Normality

```{r normality}
#| echo: false
ggplot(final_fit_aug, aes(.resid)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 1) +
  stat_function(fun = dnorm, 
    args = list(mean = mean(final_fit_aug$.resid), sd = sd(final_fit_aug$.resid)), 
    lwd = 2,  color = "red"  )
```

Independence

```{r independence}
#| echo: false
ggplot(final_fit_aug, aes(y = .resid, x = 1:nrow(final_fit_aug))) +
  geom_point(alpha = 0.5) +
  labs(x = "Order of data collection", y = "Residuals")
```
